Section_8_Team1_Lab2_Report

### 2021-08-04 reports/Draft_Report.Rmd
updated CLM section again

```{r EDA}
#Example Table
df$rural_cat <- ifelse(df$is_rural == 1, "Rural Counties", "Urban Counties")
table1::label(df$total_pop) <- "County Population"
table1::label(df$density) <- "County Population Density"
table1::label(df$cases) <- "County Covid-19 Cases"
table1::label(df$unempoy_rate) <- "County Unemployment Rate"
table1::label(df$median_income) <- "County Median Income ($)"
table1::label(df$pct_lt17) <- "County Age < 17 years (%)"
table1::label(df$pct_gt65) <- "County Age > 65 years (%)"
# table1::label(df$is_rural) <- "County Type"
table1::table1(~total_pop + density + cases + unempoy_rate + median_income + pct_lt17 + pct_gt65 | rural_cat, data = df, caption = "Table 1: Texas County Variable Statistics", topclass="Rtable1-zebra", overall = "Total")

@@

```{r Accounting Table creation & output}

df2 <- df

@@

#summary(df2)
df2 <- df2 %>% filter(!is.na(df2))
#df2 <- df2 %>% filter(!is.infinite(df2))

@@

#knitr::kable(accounting_df)
colnames(accounting_df) <- c('Step','Number of Samples','Samples Removed', 'Reason')
knitr::kable(accounting_df, caption="Accounting Table", align = "c")

@@

#need to change these to per capita data
model1 <- lm(log(long_trip+1) ~ log(cases+1) + log(deaths+1) + is_rural + median_income, data = df) #limited model
model2 <- lm(log(long_trip+1) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density+1), data = df)
model3 <- lm(log(long_trip+1) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density+1) + pct_lt17, data = df) #final model

@@

#Run coeftest to show statistical significance of all variables in the model
coeftest(model3, vcov = vcovHC(model3, type="HC1"))
```

## Discussion
### Model Limitations

1. **IID Sampling:** There isn't a direct database check for this unfortunately. Looking into how this data was generated, I belive this is IID generally. The data was gathered from independent YouTube uploaders and was a random sample.
2. **No Perfect Colinearity:** Running a VIF in R in the cell below, we see the VIF score is relatively low for both predictors. Conceptually, we can see no perfect colinearity as we cannot perfectly describe the views variable in terms of average rating or vice versa. Additionally, from the last scatter plot above, we don't see a perfect linear relationship between the predictor variabls views or average rating.
3. **Linear Conditional Expectation:** 'For this assumption, we are checking the residuals for linear relationships. We can view this by plotting the residuals, as seen below. We generally see a linear line as we move across predictor values with the residuals with no strong pattern. By transforming the average rating and views (log of), we are able to see this linear relationship across all predictor values. 
4. **Homoskedastic Errors:** 'We are looking for constant error variance across the entire range of the x's ( homoskedastic errors across the range of the x's). From the residual plot below for the final model ('Final Model' figure), we can see the even or equal spread dispersion across the x values whereas with the other two models, this is not as consistent. The residual plots for the other two show increases with the value of the fitted  variables, suggesting non-constant variances in the residuals errors (or heteroscedasticity). Therefore our final model does meet this condition.  We are able to achieve this fianl plot through transfomrtion of views and average rating (log).
5. **Normally Distributed Errors:** We are looking for a normal distribution of the residuals. We use the QQ plot to investigate this assumption. For the final model, we see a nice linear line from the QQ plot whereas the other two previou models do not show this. We are able to achieve this fianl plot through transfomrtion of views and average rating (log). In conclusion, we meet this assumption with the final model ("Final Model" plot, model = model_transformviewsrating).

@@

##FINAL MODEL
par(mfrow = c(2, 2))
plot(model3, col="red") 
title("Model 2", line = -0.75, outer = TRUE)

@@

###Omitted Variable

@@

For future analysis, it is recommended that Covid-19 policy adherence data per county be incorporated into the model to increase the accuracy. While the Govenor of Texas issued detailed protocols or mandates for the state of Texas, the degree to which each county (and thus the individual residents) complied would be useful data to have if such data were to exist.

>>>>

```{r EDA, echo=FALSE, message=FALSE}
#Example Table
df$rural_cat <- ifelse(df$is_rural == 1, "Rural Counties", "Urban Counties")
table1::label(df$total_pop) <- "County Population"
table1::label(df$density) <- "County Population Density"
table1::label(df$cases) <- "County Covid-19 Cases"
table1::label(df$unempoy_rate) <- "County Unemployment Rate"
table1::label(df$median_income) <- "County Median Income ($)"
table1::label(df$pct_lt17) <- "County Age < 17 years (%)"
table1::label(df$pct_gt65) <- "County Age > 65 years (%)"
# table1::label(df$is_rural) <- "County Type"
table1::table1(~total_pop + density + cases + unempoy_rate + median_income + pct_lt17 + pct_gt65 | rural_cat, data = df, caption = "Table 1: Texas County Variable Statistics", topclass="Rtable1-zebra", overall = "Total")

@@

```{r Accounting Table creation & output}
df2 <- df

@@

#summary(df2)
df2 <- df2 %>% filter(!is.na(df2))

#df2 <- df2 %>% filter(!is.infinite(df2))

@@

colnames(accounting_df) <- c('Step','Number of Samples','Samples Removed', 'Reason')
knitr::kable(accounting_df, caption="Accounting Table", align = "c")

@@

#need to change these to per capita data
model1 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income, data = df) #limited model
model2 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density), data = df)
model3 <- lm(log(long_trip) ~ log(cases+1) + log(deaths+1) + is_rural + median_income + unempoy_rate + log(density) + pct_lt17 + pct_gt65, data = df) #final model

@@

#Run coeftest to show statistical significance of all variables in the model with robust standard errors
coeftest(model3, vcov = vcovHC(model3, type="HC1"))

## Discussion

### Model Limitations

1. **IID Sampling:** There isn't a direct database check for this unfortunately. Looking into how the data was generated, we believe this is IID generally. The data was gathered from independent surveys within the Texas population for all models generated.

2. **No Perfect Colinearity:** This can be assessed through the variance inflation factor (VIF). Running a VIF in R in the cell below, we see the VIF score is relatively low for most predictors excluding the transformed Population Density variable. Additionally, when we view the relationship

```{r VIF & correlation}

#create vector of VIF values
vif_values2 <- car::vif(model2)
vif_values2
vif_values3 <- car::vif(model3)
vif_values3

#Put values into nicer format table
```

3. **Linear Conditional Expectation:** 'For this assumption, we are checking the residuals for linear relationships. We can view this by plotting the residuals, as seen below in the first scatter plot for both model 2 and model 3 (Residual vs Fitted). We generally see a linear line as we move across predictor values with the residuals with no strong pattern. By transforming the average rating and views (log of), we are able to see this linear relationship across all predictor values.

4. **Homoskedastic Errors:** 'We are looking for constant error variance across the entire range of the x's ( homoskedastic errors across the range of the x's). From the residual plot below for the final model ('Final Model' figure), we can see the even or equal spread dispersion across the x values whereas with the other two models, this is not as consistent. The residual plots for the other two show increases with the value of the fitted  variables, suggesting non-constant variances in the residuals errors (or heteroscedasticity). Therefore our final model does meet this condition.  We are able to achieve this fianl plot through transfomrtion of views and average rating (log).

5. **Normally Distributed Errors:** We are looking for a normal distribution of the residuals. We use the QQ plot to investigate this assumption. For the final model, we see a nice linear line from the QQ plot whereas the other two previou models do not show this. We are able to achieve this fianl plot through transfomrtion of views and average rating (log). In conclusion, we meet this assumption with the final model ("Final Model" plot, model = model_transformviewsrating).

@@

##FINAL MODEL
par(mfrow = c(2, 2))
plot(model3, col="green") 
title("Model 3", line = -0.75, outer = TRUE)

@@

### Omitted Variable

@@

For future analysis, it is recommended that Covid-19 policy adherence data per county be incorporated into the model to increase the accuracy. While the Govenor of Texas issued detailed protocols or mandates for the state of Texas, the degree to which each county (and thus the individual residents) complied would be useful data to have if such data were to exist. ***Add verbiage around including vaccine rates for next steps
